### 2021-07-23 paper.tex
biblatex style changed to numeric
certificate's department head signature
the "department head" was on a single line
leaving less space for signature, now they
are on different line.
Methodology added.
Need to put two images side by side for image acquisition section

@@

% bibliography
\usepackage[
	%backend=biber,
	style=alphabetic,
	citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

		Department Head:

@@

	\emergencystretch=1em
	\printbibliography[title={\hfill \Huge References \hfill}]

>>>>

% sub figure
\usepackage{caption}
\usepackage{subcaption}

@@

% bibliography
\usepackage[
	%backend=biber,
	style=numeric,
	citestyle=ieee
]{biblatex}
\usepackage{csquotes}

@@

		Department

		Head:

@@

	\section[methodology]{\hfill \Huge Methodology \hfill}

	As per literature survey, it was found that automated  brain  tumor
	detection  is  very  necessary  as  high accuracy is needed when human life
	is involved.  Automated detection of tumor in MR images involves feature
	extraction and  classification  using  machine  learning  algorithm.  In
	this paper, a system to automatically detect tumor in MR images is proposed
	as shown in Figure~\ref{Proposed Methodology}

	\begin{figure}[h]
		\centering
		\includegraphics[width=1\linewidth]{imgs/methodology}
		\caption{Proposed Methodology}%
		\label{Proposed Methodology}
	\end{figure}

	\textbf{ Image Acquisition: } The MRI brain images are acquired and are given as input
	to pre-processing stage. The sample brain MR images are shown in figure 2.

	%\textbf{ Preprocessing: } Preprocessing is needed as it provides improvement  in  image
	%data  which    enhances  some  of  the  image  features  which  are
	%important  for  further  processing.  The    pre-processing  steps  that
	%are  applied  to  MR  image  are as follows :

	\emergencystretch=1em
	\printbibliography[heading=bibintoc,title={References}]
